Tables/Graphs for Article

### 2018-01-02 article/draft1.Rnw
added new file

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction, and increase web traffic. This paper presents a survival analysis of response time, or the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies can investigate if factors identified as signifcant can be generalized to other CQAs.

%----------------------------------------------------------------------------------------------------

@@

As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is another important resource. This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered iPhone screens and faulty vehicle air conditioners, with over 100,000 solutions. As thousands of users rely on this forum for information, it is important that users receive timely answers. Fast response times enhance user experience and increase web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum. Analysis of response times can reveal factors that affect how quickly questions receive answered, which can lead to suggestions for how users can ask better questions to minimize response times, and for how the forum design can be improved. 
However, analysis and prediction of response times on CQAs have not been thoroughly investigated. As the majority of existing research focuses on assessing and predicting question and answer quality, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``survival'' probability of a question.

%----------------------------------------------------------------------------------------------------

@@

In regards to investigation of forum response times \cite{Bhat2014} developed a classification model to analyze response times of questions posted on \textit{Stack Overflow}, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.

\cite{Mamykina2011} found that the swift answer times of \textit{Stack Overflow's} community is a result of the reputation system and the strict emphasis on factual and informative questions and answers, rather than discussion-based.

\cite{Asaduzzaman2013} analyzed unanswered questions on \textit{Stack Overflow} to determine common characteristics and found that questions that went unanswered shared certain characteristics in that they were too short and vague, or utilized the tagging system incorrectly.

%----------------------------------------------------------------------------------------------------

@@

good question ex: id 408124, 406786 (answered)
bad question ex: id 410310, 405882 (unanswered)

The data analyzed contained 8,025 questions posted from April 8, 2017 (10:14 PM) to July 7, 2017 (9:28 PM) (the date the data was downloaded). Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date the question was posted, and date the first answer was received. Variables derived:

Categorical Variables:

\begin{itemize}
  \item Day of the week the question was posted. 
  \item Device category the question pertains to. Categories include: Apple Products, Android\/Other Phone, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle
  \item Whether or not the question's text contains any end punctuation marks (. ? !). 
  \item Whether or not the question's text is in all lower case. 
  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See appendix for a complete list of these terms. 
  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See appendix for a complete list of these terms. 
  \item Whether or not the question's title ends in a question mark.
  \item Whether or not the user edited or added information to the question's text sometime after posting it.
  \item Whether or not the user made an effort to solve the problem on their own, prior to asking the question.
\end{itemize}

Numeric Variables:

\begin{itemize}
  \item Average number of characters in each question's tags. 
  \item Average tag ``score'' for all of a question's tags. A tag score is defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a score of 0. 
  \item Number of characters in the question's text. 
  \item Number of characters in the user-defined device name. 
  \item Ratio of the number of line breaks to the number of characters in the question's text.
\end{itemize}

%----------------------------------------------------------------------------------------------------

@@

Questions analyzed were restricted to those posted in English. Time until event was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date) \cite{Kleinbaum2011}.

@@

As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions (Cox models are not based on an assumption of the shape of the underlying probability distribution) \cite{Moore2010}. To build the model, five-fold cross-validation was used. The full data was split into five training sets and five test sets \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each continuous predictor, with and without log and square root transformations, as well as each categorical predictor, was entereed into univarite Cox models, and strength of association with response times was assessed. Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include restricted cubic splines for a predictor, as well as the optimum number of knots \cite{Harrell2015}. All predictors found to be signficant, along with the transformations and functional forms found to be necessary, were included in the model for cross-validation. No variable selection was used, as \cite{Harrell2015} determined that reducing the number of predictors in the model harmed predictive accuracy, more so than leaving all predictors in.

@@

To convert the final model's predicted hazard ratios to predicted survival probability, an r function was used.

%----------------------------------------------------------------------------------------------------

\section*{Results}

@@

% Distribution of answer times
\begin{figure}[!htbp]
  \includegraphics[scale=1]{times_dist.pdf}
  \caption{Distribution of answer times}
  \label{fig:answertimes}
\end{figure}

@@

  Of 8,025 questions in the full data set, \Sexpr{nrow(x)} were in English (97\% of the full data). Of those questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date. The shortest answer time was \Sexpr{shortest} hours. The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days). Figure ~\ref{fig:answertimes} shows that the distribution of answer times for all questions is extremely right-skewed.

@@

% Table of percentiles 
\begin{table}[!h]
\centering
\begin{tabular}{rlr}
  \hline
 Percent\\ Answered & Time (hrs) \\ 
  \hline
  25 & 0.88 \\ 
  50 & 9.16 \\ 
  55 & 18.38 \\ 
  58 & 33.71 \\ 
  60 & 59.47 \\ 
  64 & 683.19 \\ 
   \hline
\end{tabular}
\caption{Table of Kaplan-Meier estimated quantiles of survival time}
\label{table:quantiles}
\end{table}

@@

% Univariate analysis on quantitative predictors
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for quantitative predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
  Predictor & p-value \\ 
  \hline \hline
  *Log transformation of the number of characters in a question's text & 0.00 \\ 
  \hline
  *Square root transformation of the number of characters in a question's text & 1.1102e-16 \\ 
  \hline
  Number of characters in a question's text (untransformed) & 6.9472e-12 \\
  \hline
  *Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 1.1488e-11 \\ 
  \hline
  *Square root transformation of the average frequency ``score'' of a question's tags & 1.4642e-11 \\ 
  \hline
  Average frequency ``score'' of a question's tags (untransformed) & 1.2706e-08 \\ 
  \hline
  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 1.3988e-7 \\ 
  \hline
  *Square root transformation of the number of characters in the user-defined device title & 2.2914e-4 \\ 
  \hline
  *Square root transformation of the average number of characters in a question's tags & 2.9999e-4 \\ 
  \hline
  Number of characters in the user-defined device title (untransformed) & 6.5304e-3 \\ 
  \hline
  Average number of characters in a question's tags (untransformed) & 2.6115e-2 \\ 
   \hline
\end{tabular}
\label{table:qresults}
\end{table}

% Univariate analysis on categorical predictors
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
 Predictor & p-value \\ 
  \hline \hline
  Device category & 0.00 \\
  \hline
  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
  \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
  \hline
  Whether or not the question's title ended in a questionmark & 1.1423e-12 \\ 
  \hline
  Whether or not the question's text contained at least one end punctuation mark & 2.5354e-9 \\ 
  \hline
  Whether or not the question's text is in all lower case & 1.5400e-7 \\ 
  \hline
  Whether or not the user edited or added information to the question's text sometime after posting it & 2.5472e-7 \\ 
  \hline
  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 3.1648e-5 \\
  \hline
  Whether or not the question's title contains terms considered to be frequently used among answered questions & 7.6397e-5 \\ 
  \hline
  Day of the week the question was posted & 7.8677e-4 \\ 
   \hline
\end{tabular}
\label{table:cresults}
\end{table}

@@

Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions. Results of univariate analysis, performed on one training set, for transformed and untransformed continuous predictors, and every categorical predictor, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively. All categorical predictors and all continuous predictors marked with * were entered into the full model.

@@

Table \ref{table:splines} shows the results of determining the optimal number of knots for each continuous predictor. Knots marked * were included in the final model.

@@

Average performance metrics for test and training sets, found in Table \ref{table:cv}, were considerably low. However, metrics did not change substantially from training to test sets, indicating that the model does not overfit. The final model, with all variables described above including splines, was fit to the full data.

@@

Assessing the proportional hazards assumption indicated that several predictors were in violation. Final model statistics and parameter coefficients are in Table \ref{table:coefficients}. Metrics for the final model's performance on the full data are found in \ref{table:finalmetrics}. The partial likelihood ratio and chi-square p-value indicate that the model as a whole is significantly associated with response time. However, the model's R^2 statistic is considerably low. Somers' Dxy and Concordance statistic are also low, and indicate low discriminative ability. Though metrics are low, metrics on the full data are not different from metrics computed in cross-validation, indicating that the model was not overfit.

The data analyzed for this model presented limitations, and may explain the model's low predictive accuracy. Many users on the CQA incorrectly specified the device name in their question (e.g. ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all. Many users also incorrectly used the tagging system---including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please\!\!\!\!\!''(tags are generally a couple key words that describe the topic of the question). These inconsistencies in the data presented some difficulties in analysis, and may explain the model's low R^2 and concordance statistics.

%----------------------------------------------------------------------------------------------------

@@

This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time. Predictors found to be signficant in the model included: device category, whether or not the question contained words considered to be ``frequently-used'' among unanswered questions, whether or not the title ends in a questionmark, whether or not the user updated the question's text after the initial posting, whether or not the user indicated that he or she made an effort prior to answer their question prior to posting it (how should I write out that different knots of the splines were signficant). While overall the model was signficant, its predictive performance was considerably low.

%----------------------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------------------

@@

<<>>=
# answered question id = 397414
index <- which(x$id == 397414)

# unanswered question id = 399971
index2 <- which(x$id == 399971)
@
%--------------------------------------------------
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|{2cm}|{2cm}|{2cm}|{2cm}}
  \hline
 Device & Title & Text & User & Date Posted & First Answer Date & Time until first answer \\
  \hline
  iPhone 6 & iPhone water damage, touch screen issue & So I dropped my iPhone in water 4 days ago. Have done the whole rice thing and seen huge difference in it. However, only one side of my screen works and it is the one side which I need to unlock the phone. What would be the best way forward? & 1 & 2017-05-10 21:50:48 GMT & 2017-05-10 23:12:27 & 1.361 hr \\ 
   \hline
\end{tabular}
\caption{Example of an answered question}
\label{table:answered_q}
\end{table}
%--------------------------------------------------
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|{2cm}|{2cm}|{2cm}|{2cm}}
  \hline
 Device & Title & Text & User & Date Posted & First Answer Date & Time until first answer \\
  \hline
  android tablet & ccccaaaan you help me fix my touch screen & touch screen not worki & 0 & 2017-05-23 07:35:12 GMT & NA & NA \\ 
   \hline
\end{tabular}
\caption{Example of an unanswered question}
\label{table:unanswered_q}
\end{table}
%--------------------------------------------------

@@

Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle. Device titles were parsed and certain categories were combined or separated to create a new category variable. Categories in the final variable included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle. Under original device categorization, 1,954 questions (25.2\% of 7,760) were not categorized correctly and indicated an NA for its category. Missing values were a result of users creating questions for devices creating questions for devices not already in the website's database, or from the user incorrectly defining the device name. For questions with missing categories, key words were searched for in device titles to recategorize accordingly.

@@

Logical variables indicating true if a question's title contained at least one of the words in the ``frequently-used'' words list for answered and unanswered questions, respectively.

These variables were created based on the hypothesis that certain question topics are more popular among the answering community, and that questions concerning these topics might receive an answer faster than questions that do not. Similarly, certain topics might be unpopular, and questions pertaining to those topics might receive answers slower than those that do (cite).

>>>>

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction, and increase web traffic. This paper presents a survival analysis of response time, or the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

%===================================================================================================
%===================================================================================================

@@

As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is another important resource. This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered iPhone screens and faulty vehicle air conditioners, with over 100,000 solutions. As thousands of users rely on this forum for information, it is important that users receive timely answers. Fast response times enhance user experience and increase web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum. Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times, and for how the forum design can be improved.

However, analysis and prediction of response times on CQAs have not been thoroughly investigated. There is need for further analysis of response times in these forums, as the majority of existing research focuses on assessing and predicting question and answer quality. This paper presents a survival analysis on the time until a question receives its first answer on iFixit's \textit{Answers} forum, in order to determine factors significantly related to answer time and to predict the ``survival'' probability of a question.

%===================================================================================================
%===================================================================================================

@@

With the recent increase in the popularity and use of CQAs, these platforms have been the subject of a multitude of studies related to information sciences. Regarding analysis of response times, \cite{Bhat2014} developed a classification model to estimate response times for questions posted on \textit{Stack Overflow}, using both tag-based and textual features. Analysis determine that tag-based features, like the number of ``popular'' tags a question contains or the number of users subscribed to a tag, were the best predictors of response time. \cite{Mahmud} proposed models based on exponential distributions to predict response times, and were built from users' previous wait times for responses. \cite{Rechavi2011} analyzed response times and satisfaction rates for questions posted on \textit{Yahoo Answers!}, and determined that the fastest times were between users who did not follow each other, while the longest times were between users who were mutual friends in the social network. \cite{Asaduzzaman2013} developed a taxonomy for classifying unanswered questions on \textit{Stack Overflow}, and developed a model to predict how long a question would remain unanswered using textual features like title and post length and whether or not the question contained code, and user features, like the number of questions asked and answered by the user prior to posting. The analysis presented in this paper seeks to analyze response time through survival analysis methods, methods that have not yet been investigated or applied to CQAs.

The majority of existing research has been focused on predicting question and answer quality by using both textual and non-textual features of posts. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com}, using primarily textual features (surface, lexical, syntactic, forum-specific, and similarity (relatedness of a post to the topic of the forum) features). \cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate metric of Wikipedia article quality. Wikipedia articles can represent the same kind of user-generated content featured on CQAs. On the other hand, \cite{H.fu} found that non-textual features, like revision and comment count on an answer or the number of points or merit badges a user has, were the most useful indicators of answer quality across four different knowledge domains on \textit{Stack Exchange}. A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question and answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a}. \cite{Ravi2014} presented a slightly different approach by analyzing the content of posts and utilizing latent topic models to predict quality. \cite{Anderson2012} developed models to the long term value of a question and its answers on \textit{Stack Overflow}. The present analysis combines both textual and non-textual features of questions on iFixit's \textit{Answers} forum in a Cox regression model to predict survival probability of questions.

%===================================================================================================
%===================================================================================================

@@

% Table of categorical predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Day of the week the question was posted \\ \hline
  Device category the question pertains to. Categories include: Android\/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
  Whether or not the question's text contains any end punctuation marks (. ? !) \\ \hline
  Whether or not the question's text is in all lower case \\ \hline
  Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See appendix for a complete list of these terms. \\ \hline
  Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See appendix for a complete list of these terms. \\ \hline
  Whether or not the question's title ends in a question mark \\ \hline
  Whether or not the user edited or added information to the question's text sometime after posting it \\ \hline
  Whether or not the user made an effort to solve the problem prior to asking the question \\ \hline
\end{tabular}
\caption{Categorical predictors derived}
\label{table:categorical}
\end{table}

% Table of quantitative predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Average number of characters in each question's tags\\ \hline
  Average tag ``score'' for all of a question's tags. A tag score is defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a score of 0. \\ \hline
  Number of characters in the question's text \\ \hline
  Number of characters in the user-defined device name \\ \hline
  Ratio of the number of line breaks to the number of characters in the question's text \\ \hline
\end{tabular}
\caption{Continuous predictors derived}
\label{table:continuous}
\end{table}

The data analyzed contained 8,025 questions posted from April 8, 2017 (10:14 PM) to July 7, 2017 (9:28 PM) (the date the data was downloaded). Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time when the question was posted, and date and time when the first answer was received. Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}. See appendix for information on how predictors were created.

%===================================================================================================
%===================================================================================================

@@

Questions analyzed were restricted to those posted in English. The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date) \cite{Kleinbaum2011}.

@@

As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}. To build the model, five-fold cross-validation was used \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each predictor was entered into univarite Cox models, and strength of association with response times was assessed. Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model. Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include into the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}. All predictors found to be signficant, along with the transformations and functional forms found to be necessary, were included in the model for cross-validation. No variable selection was used, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than leaving all predictors in.

@@

To obtain predicted survival probabilities using the model, the predictSurvProb function was used from the pec package. This function uses the Cox model and a vector of times to compute predicted survival probabilities.

%===================================================================================================
%===================================================================================================

\section*{Results and Discussion}

@@

% Distribution of answer times
\begin{figure}[!htbp]
  \includegraphics[scale=1]{times_dist.pdf}
  \caption{Distribution of response times}
  \label{fig:answertimes}
\end{figure}

@@

  Of 8,025 questions in the full data set, \Sexpr{nrow(x)} were in English (97\% of the full data). Of those questions, \Sexpr{answered} (\Sexpr{percentans}}\%) received an answer by the download date. The shortest response time was \Sexpr{shortest} hours. The longest was \Sexpr{longest} hours (\Sexpr{longest_d} days). Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

@@

% Table of percentiles 
\begin{table}[!h]
\centering
\begin{tabular}{rlr}
  \hline
 Percent\\ Answered & Time (hrs) \\ 
  \hline
  25 & 0.88 \\ 
  50 & 9.16 \\ 
  55 & 18.38 \\ 
  58 & 33.71 \\ 
  60 & 59.47 \\ 
  64 & 683.19 \\ 
   \hline
\end{tabular}
\caption{Kaplan-Meier estimated quantiles of survival time}
\label{table:quantiles}
\end{table}

@@

% Univariate analysis on quantitative predictors
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
  Predictor & p-value \\ 
  \hline \hline
  *Log transformation of the number of characters in a question's text & 0.00 \\ \hline
  *Square root transformation of the number of characters in a question's text & 1.1102e-16 \\ \hline
  Number of characters in a question's text (untransformed) & 6.9472e-12 \\\hline
  *Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 1.1488e-11 \\ \hline
  *Square root transformation of the average frequency ``score'' of a question's tags & 1.4642e-11 \\ \hline
  Average frequency ``score'' of a question's tags (untransformed) & 1.2706e-08 \\ \hline
  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 1.3988e-7 \\ \hline
  *Square root transformation of the number of characters in the user-defined device title & 2.2914e-4 \\ \hline
  *Square root transformation of the average number of characters in a question's tags & 2.9999e-4 \\ \hline
  Number of characters in the user-defined device title (untransformed) & 6.5304e-3 \\ \hline
  Average number of characters in a question's tags (untransformed) & 2.6115e-2 \\ \hline
\end{tabular}
\label{table:qresults}
\end{table}

% Univariate analysis on categorical predictors
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
 Predictor & p-value \\ 
  \hline \hline
  Day of the week the question was posted & 7.8677e-4 \\ \hline
  Device category & 0.00 \\ \hline
  Whether or not the question's text contained at least one end punctuation mark & 2.5354e-9 \\ \hline
  Whether or not the question's text is in all lower case & 1.5400e-7 \\ \hline
  Whether or not the question's title contains terms considered to be frequently used among answered questions & 7.6397e-5 \\ \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ \hline
  Whether or not the question's title ended in a questionmark & 1.1423e-12 \\ \hline
  Whether or not the user edited or added information to the question's text sometime after posting it & 2.5472e-7 \\ \hline
  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ \hline
  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 3.1648e-5 \\ \hline

\end{tabular}
\label{table:cresults}
\end{table}

% Univariate analysis on quantitative predictors
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
\begin{tabular}{| p{5cm} | l | l |}
  \hline
  Predictor & Transformation & p-value \\ 
  \hline
  \multirow{3}{5cm}{Average number of characters in each questions tags}
  & Untransformed & 2.6115e-2 \\ 
  & Log & NA \\
  & Square root & 2.9999e-4 \\ \hline
  \multirow{3}{5cm}{Average frequency score of a question’s tags}
  & Untransformed & 1.2706e-08 \\
  & Log & NA \\
  & Square root & 1.4642e-11 \\ \hline
  \multirow{3}{5cm}{Number of characters in a question's text}
  & Untransformed & 6.9472e-12 \\
  & Log & 0.00 \\
  & Square root & 1.1102e-16 \\ \hline
  \multirow{3}{5cm}{Number of characters in the user-defined device title}
  & Untransformed & 6.5304e-3 \\
  & Log & NA \\
  & Square root & 2.2914e-4 \\ \hline
  \multirow{3}{5cm}{Ratio of the number of line breaks to the number of characters in a question's text} 
  & Untransformed & 1.3988e-7 \\
  & Log & NA \\
  & Square root & 1.1488e-11 \\ \hline
\end{tabular}
\label{table:qresults}
\end{table}

@@

Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions. Results of univariate analysis, performed on one training set, for transformed and untransformed continuous predictors, and every categorical predictor, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively. All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.

@@

Table \ref{table:splines} shows the results of determining the optimal number of knots for each continuous predictor. Values of knots marked with an asterisk (*) were included in the final model.

@@

Average performance metrics for test and training sets and in Table \ref{table:cv}. Partial likelihood ratio statistics and p-values indicate that the model as a whole is signficantly associated with response time. However, its R^2 statistic and discrimination indexes are considerably low. Metrics did not change significantly from training to test sets, indicating that the model was not overfit.

@@

Assessing the proportional hazards assumption indicated that several predictors were in violation, results can be found in Table \ref{table:ph_assumption}. Final model statistics and parameter coefficients are in Table \ref{table:coefficients}. Metrics for the final model's performance on the full data are found in \ref{table:finalmetrics}, and are consistent with the metrics found in cross validation---the model as a whole is significantly associated with response time, but has a low $R^2$ statistic and indicates low discriminative ability. Individual predictors found to be significant (alpha = 0.001) are: device category, whether or not the question's text contains ``frequently-used'' terms among unanswered questions, whether or not the questions title ends in a questionmark, whether or not the user updated the question after posting it.

The data analyzed for this model presented limitations, and may explain the model's low predictive accuracy. Many users on the CQA incorrectly specified the device name in their question (e.g. ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all. Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!''(tags are generally a couple key words that describe the topic of the question). These inconsistencies in the data presented some difficulties in analysis, and may explain the model's low R^2 and discrimination indexes.

Future studies can further investigate if the predictors found to be significant in this study can be generalized to other CQAs.

%===================================================================================================
%===================================================================================================

@@

This study developed a Cox proportional hazards model to predict the probability that a question posted on iFixit's \textit{Answers} forum receives an answer before a certain time. Predictors found to be signficant in the model included: device category, whether or not the question contained words considered to be ``frequently-used'' among unanswered questions, whether or not the title ends in a questionmark, and whether or not the user updated the question's text after the initial posting. While overall the model was signficant, its predictive performance was considerably low.

%===================================================================================================
%===================================================================================================

@@

%===================================================================================================
%===================================================================================================

@@

<< echo = FALSE >>=
# answered question id = 397414
index <- which(x$id == 397414)

# unanswered question id = 399971
index2 <- which(x$id == 399971)
@

% Table to display an answered question---------------------------------
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|{2cm}|{2cm}|{2cm}|{2cm}}
  \hline
 Device & Title & Text & User & Date Posted & First Answer Date & Time until first answer \\
  \hline
  iPhone 6 & iPhone water damage, touch screen issue & So I dropped my iPhone in water 4 days ago. Have done the whole rice thing and seen huge difference in it. However, only one side of my screen works and it is the one side which I need to unlock the phone. What would be the best way forward? & 1 & 2017-05-10 21:50:48 GMT & 2017-05-10 23:12:27 & 1.361 hr \\ 
   \hline
\end{tabular}
\caption{Example of an answered question}
\label{table:answered_q}
\end{table}

% Table to display an unanswered question-------------------------------
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{2cm}|p{3cm}|p{6cm}|{2cm}|{2cm}|{2cm}|{2cm}}
  \hline
 Device & Title & Text & User & Date Posted & First Answer Date & Time until first answer \\
  \hline
  android tablet & ccccaaaan you help me fix my touch screen & touch screen not worki & 0 & 2017-05-23 07:35:12 GMT & NA & NA \\ 
   \hline
\end{tabular}
\caption{Example of an unanswered question}
\label{table:unanswered_q}
\end{table}
%-----------------------------------------------------------------------

@@

\begin{itemize}
  \item Original device categories, defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle. Device titles were parsed and certain categories were combined or separated to create a new device categorization. Categories in the final variable included: Android/Other Phone, Apple Product, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle. Under original device categorization, 1,954 questions (25.2\% of 7,760) were not categorized correctly and indicated an NA for its category. Missing values were a result of users creating questions for devices not already in the iFixit's database, or from the user incorrectly defining the device name. For questions with missing categories, key words were searched for in device titles to recategorize accordingly. 
\end{itemize}

%-----------------------------------------------------------------------

@@

\begin{itemize}
  \item Logical variables indicating true if a question's title contained at least one of the words in the ``frequently-used'' words list for answered and unanswered questions, respectively. 
  \item These variables were created based on the hypothesis that certain question topics are more popular among the answering community, and that questions concerning these topics might receive an answer faster than questions that do not. Similarly, certain topics might be unpopular, and questions pertaining to those topics might receive answers slower than those that do not (cite).
  \item To create the variables, the data was separated between answered and unanswered questions. For the data frame containing answered questions, text mining techniques were used to create a list of every word within each questions' titles and the frequency, or proportion of times those words occurred among all answered questions' titles. The same was performed for the data frame containing unanswered questions. ``Frequently-used'' words in answered questions were defined as those that appeared in more than 1\% of all answered questions' titles, and appeared in more answered questions than in unanswered questions. To determine the latter, a ratio of frequencies, or proportions of times a word occurs, was assessed. The ratio was calculated as the proportion of time a word occured among answered questions, to the proportion of times a word occured in unanswered questions. As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered ``frequently-used'' among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20). Similarly, ``frequently-used'' words in unanswered questions must occur in 1\% or more of all unanswered question's titles and occur in more unanswered questions than answered questions. As there was some overlap between ``frequently-used'' words in each list and the device categories, every word that matched a device name was removed from the lists. The resulting list for answered questions contained 111 words. The list for unanswered questions contained 32 words. Lists can be found in Table \ref{table:frequent_terms}
\end{itemize}
